Formulating RDF Constraints and \\ Validating RDF Data Generically

### 2015-04-20 paper/paper 2/paper 2.tex
simple constraints

\subsection{Simple Constraints (Expressible in DL)}

Sub-classes of \textbf{\emph{simple constraints}} are \textbf{\emph{property constraints}} and \textbf{\emph{class constraints}} (see the \emph{RDF-CV} implementation model in figure \ref{fig:RDF-CV-implementation-model}). 
For both \emph{property} and \emph{class constraints} a \emph{context class}, a list of \emph{classes}, the \emph{constraining element}, and the \emph{constraining value} can be stated. 
Lists of \emph{left} and \emph{right properties} can only be stated for \emph{property constraints}.

@@

A constraint holds for all individuals of a \emph{context class} (\textbf{\emph{contextClass}}).
Consider, e.g., the following minimum qualified cardinality restriction on the object property \emph{author}, which restricts \emph{publications} to have at least one \emph{author} which is a \emph{person}: 
\begin{DL}
$Publication \sqsubseteq \geq1 author . Person $
\end{DL}
Mapped to the \emph{RDF-CV} (see table \ref{tab:property-constraint-cardinality-restriction}), the cardinality restriction is classified as a \emph{property constraint} which holds for all individuals of the class \emph{Publication}:

@@

The \emph{constraining element} (\textbf{\emph{constrainingElement}}) indicates the actual type of constraint like DL concept and role constructors, (in)equality, and further keywords for constraint types which cannot be expressed in DL (e.g. regular expressions and constraining facets).
In some cases, a constraint is only complete when in addition to the \emph{constraining element} a \emph{constraining value} (\textbf{\emph{constrainingValue}}) is stated.
The cardinality restriction 
\ms{$\geq$1 author.Person}, e.g., 
constructs an anonymous class of all individuals having at least one \emph{author} relationship to \emph{persons}.
The \emph{constraining element} of this \emph{property constraint} is the DL at-least restriction \emph{$\geq$} and the \emph{constraining value} is \emph{1}.
\textbf{\emph{Classes}} indicate the list of classes, constraints refer to.
The qualified cardinality restriction above, e.g., refers to the class \emph{Person}, 
i.e. restricts the objects, the property \emph{author} points to, to be of the class \emph{Person}.

For \emph{property constraints}, \emph{left} and \emph{right property lists} (\textbf{\emph{leftProperties}}, \textbf{\emph{rightProperties}}) are specified.
The assignment of properties to these lists happens relative to the \emph{constraining element} - which may be an operator (e.g. $\sqsubseteq$ in case of object property paths).
\emph{Object Property Paths}\footnote{Corresponds to the requirement \emph{R-55-OBJECT-PROPERTY-PATHS}} (also called \emph{complex role inclusion axioms} in DL terminology)
state that, if an individual \emph{x} is connected by a sequence of object properties with an individual \emph{y}, 
then \emph{x} is also connected with \emph{y} by a particular object property. 
According to the following object property path and some instance data, \emph{Stephen-Hawking} is an author of the genre \emph{Popular-Science} 
(as \emph{Stephen-Hawking} is an author of the book \emph{A-Brief-History-Of-Time} whose genre is \emph{Popular-Science}):

@@

When mapped to the \emph{RDF-CV} (see table \ref{tab:property-constraint-object-property-paths}), the properties \emph{authorOf} and \emph{genre} are on the left side of the \emph{constraining element} \emph{$\sqsubseteq$},
and the property \emph{authorOfGenre} is on the right side:

@@

\subsection{Simple Constraints (Not Expressible in DL)}

@@

\subsection{Complex Constraints}

@@

\subsection{Complex Constraints as Simple Constraints (Syntactic Sugar)}

>>>>

\subsection{\emph{Simple Constraints} (Expressible in \emph{DL})}

Sub-classes of \textbf{\emph{simple constraints}} are \textbf{\emph{property constraints}} and \textbf{\emph{class constraints}} (see the \emph{RDF-CV} implementation model in figure \ref{fig:RDF-CV-implementation-model}). 
For both \emph{property} and \emph{class constraints} a \emph{context class}, a list of \emph{classes}, the \emph{constraining element}, and the \emph{constraining value} can be stated. 
Lists of \emph{left} and \emph{right properties} can only be specified for \emph{property constraints}.

@@

A \emph{simple constraint} holds for all individuals of a \textbf{\emph{context class}}.
Consider, e.g., the following \emph{minimum qualified cardinality restriction} on the object property \emph{author}, which restricts \emph{publications} to have at least one \emph{author} which is a \emph{person}: 
\begin{DL}
$Publication \sqsubseteq \geq1 author . Person $
\end{DL}
The cardinality restriction is a constraint on the property \emph{author} and is therefore classified as a \emph{property constraint} which holds for all individuals of the class \emph{Publication} (see table \ref{tab:property-constraint-cardinality-restriction} for the mapping to \emph{RDF-CV}):

@@

The \textbf{\emph{constraining element}} indicates the actual type of constraint like \emph{DL} concept and role constructors, (in)equality, and further keywords for constraint types which cannot be expressed in \emph{DL} (e.g. regular expressions and constraining facets).
In some cases, a constraint is only complete when in addition to the \emph{constraining element} a \textbf{\emph{constraining value}} is stated.
The cardinality restriction 
\ms{$\geq$1 author.Person}, e.g., 
constructs an anonymous class of all individuals having at least one \emph{author} relationship to \emph{persons}.
The \emph{constraining element} of this \emph{property constraint} is the \emph{DL} at-least restriction \emph{$\geq$} and the \emph{constraining value} is \emph{1}.
\emph{Simple constraints} may refer to a list of \textbf{\emph{classes}}.
The qualified cardinality restriction above, e.g., refers to the class \emph{Person}, 
i.e. restricts the objects of the property \emph{author} to be of the class \emph{Person}.

For \emph{property constraints}, \textbf{\emph{left}} and \textbf{\emph{right property lists}} are specified.
The assignment of properties to these lists happens relative to the \emph{constraining element} - which may be an operator (e.g., $\sqsubseteq$ in case of \emph{object property paths}).
\emph{Object Property Paths}\footnote{Corresponds to the requirement \emph{R-55-OBJECT-PROPERTY-PATHS}} (also called \emph{complex role inclusion axioms} in \emph{DL})
express that, if an individual \emph{x} is connected by a sequence of object properties with an individual \emph{y}, 
then \emph{x} is also related to \emph{y} by a particular object property. 
As \emph{Stephen-Hawking} is the \emph{author} of the book \emph{A-Brief-History-Of-Time} (\ms{authorOf(Stephen-Hawking, A-Brief-History-Of-Time)}) whose \emph{genre} is \emph{Popular-Science} ({\ms{genre(A-Brief-History-Of-Time, Popular-Science)}),
the following \emph{object property path} infers that \emph{Stephen-Hawking} is an \emph{author} of the \emph{genre} \emph{Popular-Science} (\ms{authorOfGenre(Stephen-Hawking, Popular-Science)}):

@@

Thus, when mapped to the \emph{RDF-CV} (see table \ref{tab:property-constraint-object-property-paths}), the properties \emph{authorOf} and \emph{genre} are on the left side of the \emph{constraining element} \emph{$\sqsubseteq$},
and the property \emph{authorOfGenre} is on the right side:

@@

\subsection{\emph{Simple Constraints} (Not Expressible in \emph{DL})}

@@

\subsection{\emph{Complex Constraints}}

@@

\subsection{\emph{Complex Constraints} as \emph{Simple Constraints} (Syntactic Sugar)}
